Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-03-18 docs/manuscript/main.tex
fused fig6and7 into fig06 and ammends captions and fixes references

\subsection*{3D RQA ENTR}
As ENTR appeared to be have higher sensitivity than the other measures, 
we explored the impact of different embedding parameters 
$ \{ m \in \mathbb{R} | 1 \le m \le 10  \} $,
$  \{ \tau \in \mathbb{R} | 1 \le \tau \le 10  \} $ 
incrementing by 1 each run, with recurrence thresholds $\epsilon=1, 2, 3$ 
and levels of smoothness (sg0, sg1, sg2).  
Figure \ref{fig:RQA-IND} shows that increasing recurrence 
threshold leads to an increase in ENTR regardless of level of smoothness.  
Similarly, increasing level of smoothness will also increase ENTR (figure \ref{fig:RQA-IND}).
In terms of movement or performer, RQA ENTR decrease from Slow (HS, VS) to Fast (HF, VF) 
for both human (HS01) and (RS01) (Figures~\ref{fig:3dRQAENTR_sensoractivities}).
In terms of individual differences, for human participants, 
figure \ref{fig:3dRQAENTR_participantsactivities} compares p01, p02 and p03 (for illustrative purposes) --
both between each other and in comparison with the more consistent performance of the robot.  
In terms of window length (w100 (2s), w250 (5s), w500(10s), w750 (15s)), 
figure \ref{fig:3dRQAENTR_windowsactivities} shows that improvement in 
capture with number of samples, although this has less of an effect on RQA ENTR.

%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{figures/rqa/output/rqa-epsilons}
    \caption
	[3D surface plots of RQA ENTR values]{
	{\bf 
	3D surface plots of RQA ENTR values for different recurrence threshold and smoothness levels.}
	RQA ENTR values are
	for embedding parameters
	$ \{ m \in \mathbb{R} | 0 \le m \le 10  \} $,
	$ \{ \tau \in \mathbb{R} | 0 \le \tau \le 10  \} $
	incrementing by one and three recurrence thresholds $\epsilon=1, 2, 3$.
	RQA ENTR values were computed with data from $p03$, sensor HS01, with 
	a window size of 10-secs (500 samples).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig:RQA-IND}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------

%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rqa/output/rqa-sensors-activities}
    \caption{
	{\bf 3D surface plots of RQA ENTR values for different sensors and activities.}
	RQA ENTR values are for embedding parameters
	$ \{ m \in \mathbb{R} | 0 \le m \le 10  \}$,
	$ \{ \tau \in \mathbb{R} | 0 \le \tau \le 10  \}$
	with $\epsilon = 1 $ considering four activities 
	Horizontal Normal (HN), Horizontal Faster(HF), Vertical Normal(VN), and 
	Vertical Faster (VF) and sensors Human Sensor 01 (HS01) and 
	Robot Sensor (RS01).
	RQA ENTR values were computed from data of $p03$, sg0 and 
	window size of 10-secs (500 samples).
	Code and data to reproduce the figure is available in \cite{srep2021}.
       }
\label{fig:3dRQAENTR_sensoractivities}
\end{figure}
%%---------------------------------(FIGURE)-------------------------------------

>>>>

\subsection*{3D RQA ENTR}
As ENTR appeared to be have higher sensitivity than the other measures, 
we explored the impact of different embedding parameters 
$ \{ m \in \mathbb{R} | 1 \le m \le 10  \} $,
$  \{ \tau \in \mathbb{R} | 1 \le \tau \le 10  \} $ 
incrementing by 1 each run, with recurrence thresholds $\epsilon=1, 2, 3$ 
and levels of smoothness (sg0, sg1, sg2).  
Figure \ref{fig06}(A) shows that increasing recurrence
threshold leads to an increase in ENTR regardless of level of smoothness.  
Similarly, increasing level of smoothness will also increase ENTR (figure \ref{fig06}(A)).
In terms of movement or performer, RQA ENTR decrease from Slow (HS, VS) to Fast (HF, VF) 
for both human (HS01) and (RS01) (Figures~\ref{fig06}(B)).
In terms of individual differences, for human participants, 
figure \ref{fig:3dRQAENTR_participantsactivities} compares p01, p02 and p03 (for illustrative purposes) --
both between each other and in comparison with the more consistent performance of the robot.  
In terms of window length (w100 (2s), w250 (5s), w500(10s), w750 (15s)), 
figure \ref{fig:3dRQAENTR_windowsactivities} shows that improvement in 
capture with number of samples, although this has less of an effect on RQA ENTR.

%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{figures/fig06/versions/drawing-v00}
    \caption
	[3D surface plots of RQA ENTR values]{
	{\bf 
	3D surface plots of RQA ENTR values for different recurrence threshold and smoothness levels (A) and for different sensors and activities (B).}
	RQA ENTR values are for embedding parameters $ \{ m \in \mathbb{R} | 0 \le m \le 10  \} $, $ \{ \tau \in \mathbb{R} | 0 \le \tau \le 10  \}$ incrementing by one and three recurrence thresholds $\epsilon=1, 2, 3$.
	RQA ENTR values were for A were computed with data from $p03$, sensor HS01, with a window size of 10-secs (500 samples).
	RQA ENTR values are for embedding parameters $ \{ m \in \mathbb{R} | 0 \le m \le 10  \}$, $ \{ \tau \in \mathbb{R} | 0 \le \tau \le 10  \}$ with $\epsilon = 1 $ considering four activities: Horizontal Normal (HN), Horizontal Faster(HF), Vertical Normal(VN), Vertical Faster (VF), and sensors: Human Sensor 01 (HS01) and Robot Sensor (RS01).
	RQA ENTR values for B were computed from data of $p03$, sg0 and window size of 10-secs (500 samples).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig06}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------

%%%---------------------------------(FIGURE)-------------------------------------
%\begin{figure}[ht]
%\centering
%\includegraphics[width=1.0\textwidth]{figures/rqa/output/rqa-sensors-activities}
%    \caption{
%	{\bf 3D surface plots of RQA ENTR values for different sensors and activities.}
%	RQA ENTR values are for embedding parameters
%	$ \{ m \in \mathbb{R} | 0 \le m \le 10  \}$,
%	$ \{ \tau \in \mathbb{R} | 0 \le \tau \le 10  \}$
%	with $\epsilon = 1 $ considering four activities
%	Horizontal Normal (HN), Horizontal Faster(HF), Vertical Normal(VN), and
%	Vertical Faster (VF) and sensors Human Sensor 01 (HS01) and
%	Robot Sensor (RS01).
%	RQA ENTR values were computed from data of $p03$, sg0 and
%	window size of 10-secs (500 samples).
%	Code and data to reproduce the figure is available in \cite{srep2021}.
%       }
%\label{fig:3dRQAENTR_sensoractivities}
%\end{figure}
%%%---------------------------------(FIGURE)-------------------------------------
